An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-02-08 tex/paper.tex
Adding an abstract.

>>>>

\begin{abstract}
    The Axelrod Python library is an open source package that allows for
    reproducible game theoretic research in to the iterated Prisoner's Dilemma.
    This area of research began in the 1980 but suffers from a lack of
    documented and tested code. This library aims to address this.

    With a growing collection of 120 strategies the library is also a platform
    for an original tournament that in itself is of interest to the game
    theoretic community.
\end{abstract}
